\bf Supplementary Material: What is the Best Way to Display Two Time Series to Read Association?

### 2016-01-27 paper/supplementary.Rnw
supplementary

\begin{figure}[htbp]
\centering
<<users, dependson='setup', echo=FALSE, results='asis', fig.height=3, message=FALSE, error=FALSE, warning=FALSE>>=
users <- read.csv("turk18_users.csv")
users$academic_study <- factor(users$academic_study)
levels(users$academic_study) <- c("At Most High School", "Some Undergraduate", "Undergraduate Degree", "Some Postgraduate", "Postgraduate Degree")
users$age <- factor(users$age)
levels(users$age) <- c("18-25", "26-30", "31-35", "36-40", "41-45", "46-50", "51-55", "56-60", "61+")
ggplot(data=users, aes(x=age, fill=academic_study)) + geom_bar() + facet_wrap(~gender) +
  scale_fill_manual(name = element_blank(), values=c("#550000", "#883388", "#1133FF", "#FF9933", "#555555")) + labs(x="Age", y=element_blank()) + theme(axis.text.x = element_text(angle = 270))
@
\caption{Age and education by gender. Most subjects are in the younger brackets and there are more males than females}
\label{ageed}
\end{figure}

This section describes the demographics of the subjects in the experiment recruited through Amazon's Mechanical Turk. Age, gender, education and location all did not have a statistically significant effect on the selections made.

\section{Descriptive Statistics of Evaluations}

\begin{figure}[h]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
full$choice_reason <-sapply(strsplit(as.character(unlist(full$choice_reason)), "[^0-9]+"), "[[", 1)
choice <- full %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
choice$choice_reason <- factor(choice$choice_reason)
levels(choice$choice_reason) <- c("Close Together", "Matching Peaks", "Pattern Formed", "Formed a line", "Other")
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@
\caption{Reasons given for plot selection. After controlling for lineup factors, any explanatory power of the reason is removed.}
\label{reasons}
\end{figure}

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=factor(r), fill=design)) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
@
\caption{Characteristics of lineups with at least one subject making multiple selections. Overlaid lines lineups have multiple selections more often, and true plot correlation does not appear to have an impact except at large sample sizes.}
\label{lineupmulti}
\end{figure}

\begin{table}[h]
\caption{Number of selections for each lineup evaluation. The subject with the most selections is additionally reported.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\iffalse
\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{table}}
\label{attemptshist}
\end{figure}
\fi

@@

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>= 
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.1)
@
\caption{The average score of our subjects, according to formula \ref{score}. There is a wide range of visual ability to be controlled with random effects in the modelling}
\label{avscore}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
<<users, dependson='setup', echo=FALSE, results='asis', fig.height=3, message=FALSE, error=FALSE, warning=FALSE>>=
users <- read.csv("turk18_users.csv")
users$academic_study <- factor(users$academic_study)
levels(users$academic_study) <- c("At Most High School", "Some Undergraduate", "Undergraduate Degree", "Some Postgraduate", "Postgraduate Degree")
users$age <- factor(users$age)
levels(users$age) <- c("18-25", "26-30", "31-35", "36-40", "41-45", "46-50", "51-55", "56-60", "61+")
ggplot(data=users, aes(x=age, fill=academic_study)) + geom_bar() + facet_wrap(~gender) +
  scale_fill_manual(name = element_blank(), values=c("#550000", "#883388", "#1133FF", "#FF9933", "#555555")) + labs(x="Age", y=element_blank()) + theme(axis.text.x = element_text(angle = 270))
@
\caption{Age and education by gender. Younger age brackets and males are over-represented in the sample, but these factors caused no significant impact on results.}
\label{ageed}
\end{figure}

Despite there being a wide range of subject demographics in the experiment recruited through Amazon's Mechanical Turk, age, gender, education and location all did not have a statistically significant effect on power of either plot design.

@@

\begin{figure}[htbp]
\centering 
<<avscore, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=4>>= 
subjplot <- summarise(group_by(full.sub, subj_id), eval=sum(weights), total = sum(score))
subjplot <- mutate(subjplot, avscore= total/eval)
ggplot(data=subjplot, aes(x=avscore)) + geom_histogram(binwidth=0.1)
@
\caption{The average score of our subjects, according to formula \ref{score}. There is a wide range of visual ability to be controlled with random effects in the modelling}
\label{avscore}
\end{figure}

\section{Evaluation Descriptive Statistics}

\begin{figure}[h]
\centering
<<choices, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=4>>=
full$choice_reason <-sapply(strsplit(as.character(unlist(full$choice_reason)), "[^0-9]+"), "[[", 1)
choice <- full %>% transform(choice_reason= strsplit(as.character(choice_reason), "")) %>% unnest(choice_reason)
choice$rsgn <- factor(choice$rsgn, labels=c("r -","r +"))
choice$correct <- factor(choice$correct, labels=c("Did not detect", "Detected"))
choice$choice_reason <- factor(choice$choice_reason)
levels(choice$choice_reason) <- c("Close Together", "Matching Peaks", "Pattern Formed", "Formed a line", "Other")
ggplot(data=choice, aes(x=choice_reason, fill=correct)) + geom_bar() + facet_grid(design~rsgn) +
  theme(legend.position="bottom", axis.title=element_blank()) + scale_fill_discrete(name="True Plot")
@
\caption{Reasons given for plot selection. After controlling for lineup factors, there is no explanatory power.}
\label{reasons}
\end{figure}

\begin{figure}[htbp]
\centering
<<multiselect, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=4>>=
m.select <- summarise(group_by(subset(full.sub, attempts>1), subj_id, pic_id), attempts=max(attempts))
m.freq <- data.frame(table(m.select$pic_id))
m.lineup <- merge(m.freq, bylineup, by.x="Var1", by.y="pic_id")
ggplot(data=m.lineup) + geom_bar(aes(x=factor(r), fill=design)) + facet_grid(n~smoothed) + labs(y="Count", x="True plot correlation")
@
\caption{Characteristics of lineups with at least one subject making multiple selections. Overlaid line lineups have multiple selections more often, and true plot correlation does not appear to have an impact except at large sample sizes.}
\label{lineupmulti}
\end{figure}

\begin{table}[h]
\centering
\caption{Number of times $n$ selections from a lineup evaluation were made. The subject who made the most selections is additionally reported. There is no relationship between a subject's demographics and a likelihood to make multiple selections.}
\label{table}
<<tabattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
attempts <- summarise(group_by(full.sub, subj_id, pic_id), attempts = max(attempts))
attempts.table <- data.frame(table(attempts$attempts))
attempts.table$most <- c(0,0,0,5,3,1,1)
colnames(attempts.table) <- c("Selections", "Whole Sample", "Subject 123")
kable(attempts.table, format="latex")
@
\end{table}

\iffalse
\begin{figure}[htbp]
\centering
<<multiattempts, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE, fig.height=4>>=
ggplot(data=attempts) + geom_bar(aes(x=as.factor(attempts))) + labs(x="Number of selections", y=NULL)
@
\caption{Histogram of table~\ref{table}}
\label{attemptshist}
\end{figure}
\fi
